%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Mohd Arshul}{Mansoori}{ \urlstyle{same}
\href{mailto:arshulmohd123@gmail.com}{arshulmohd123@gmail.com} |+91 981.871.0556}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary} 
\location{I am a passionate developer, who loves solving problems and working with product-based start-ups and Open-Source organizations. Primarily working on Web/Mobile based applications and DevOps.}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
Github:// \href{https://github.com/arshul}{\custombold{arshul}} \\
LinkedIn://  \href{https://www.linkedin.com/in/arshul}{\custombold{arshul}}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Programming}
\location{Languages:}
JavaScript \textbullet{} Python \textbullet{} Shell \\
\location{Frameworks:}
ReactJs \textbullet{} NodeJs \textbullet{} ReactNative \textbullet{} Flask \\ 
Semantic UI \textbullet{} Bootstrap \\
\location{Tools and Technologies:}
Docker \textbullet{} Git \textbullet{} Terraform \\ GraphQL \textbullet{} PostgreSQL \textbullet{} MongoDB \\
Linux/Unix \textbullet{} AWS \textbullet{} HTML/CSS \\ 
\location{Familiar:}
Puppet \textbullet{} Ansible \textbullet{} JQuery\\
\subsection{Soft Skills}
\location{Problem Solving\\ Quick Learning \\ Debugging \\ Logical Thinking \\  Research Orientation }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{AIACTR, GGSIPU}
\descript{B.Tech CSE}
\location{Grad. 2020 | Delhi, IN \\ CGPA: 7.1}
\sectionsep

\subsection{Andhra Education Society}
\descript{Class 12, CBSE}
\location{Grad. May 2015 | Delhi, IN \\ Percentage: 78.00}
\sectionsep


\section{Awards} 
\subsection{SIGHPC Travel Grant}
SIGHPC provides travel grant to students from all over the world to attend the SUPERCOMPUTING CONFERENCE series.
I was one of the four recipients from around the world to attend SC19 in Denver,Colorado.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Google Summer of Code}
\descript{| Student Developer }
\location{ May 2020 – Aug 2020 (Remote) | Canadian Centre for Computational Genomics }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Fixed Terraform config files to fix broken builds of HPC infrastructure \& fixed ZFS installation.
\item Setup BeeGFS file system on the stack manually and automatically.
\item Added new nodes based on a configuration setting from the user.
\item Ensured CVMFS stack present on the deployed HPC stack.

\end{tightemize}
\sectionsep

\runsubsection{Google Summer of Code}
\descript{| Student Developer }
\location{ May 2019 – Aug 2019 (Remote) | CROSS, UC Santa Cruz }
\begin{tightemize}
\item Developed GitHub actions and example scientific workflows using Docker and Shell script.
\item Worked on workflows for the Student Cluster Competition reproducibility challenge of SC18 and SC19.
\item Added functionalities to the CLI based execution engine.
\item Developed and published a python package to PyPI.
\end{tightemize}
\sectionsep

\runsubsection{Learncool}
\descript{| Full Stack Software Engineering Intern }
\location{ Jun 2018 – Mar 2019 (Remote) | Singapore}
\begin{tightemize}
\item Developed GraphQL APIs in NodeJs and consumed them in ReactJs.
\item  Implemented group-chat using web-sockets and added a feature to send an image
in a message.
\item Established Flask app to send emails via API.
\item Contributed in developing required new features in the web application
\end{tightemize}
\sectionsep

\runsubsection{Travel D'globe}
\descript{| Full Stack Developer Intern }
\location{Jul 2017 – Apr 2018 | Delhi, IN}
\begin{tightemize}
\item Developed REST APIs in Flask and Django.
\item Scraped websites using Beautiful-Soup and Selenium and stored them in MongoDB and PostgreSQL.
\item Integrated payment-gateway (RazorPay).
\item Built responsive web pages for the web applications.
\item Automated reading and replying of WhatsApp messages using Selenium and Natural Language Processing. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     START-UP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Start-up}
\runsubsection{Bird Infotech and Resource Developer}
\descript{| Co-Founder}
\location{Sept 2019 – Apr 2020}
\begin{tightemize}
\item Hired and Led the Technical team of the company.
\item Developed, Managed and Deployed Multiple Backend Micro-service applications.
\item Planned strategies to increase customer base and improve relations.
\item Held meetings with clients and early investors
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership}
\runsubsection{*A Political Party*}
\descript{| Technical Lead \& Mentor}
\location{ Apr 2019 – Aug 2019 }
Created multiple products from scratch to help the internal functioning of a party, also interviewed and managed summer interns as an IT Dept. Mentor.
\sectionsep

\end{minipage} 
\end{document}